---
title: 'Machine Learning: Exercise 0'
author: "Lorenz Bacca & Nesrine Haddar"
date: "22.10.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(ggplot2)
dataset1 <- fread("FacultySalaries.csv")
```

## Faculty Salaries

The dataset has 50 observations and 6 columns including the target variable.

#### asst.prof.salary
The target variable is **asst.prof.salary** and is numeric. It's values range from 35.30 to 56.40 with a mean of 43.28 and a median of 42.45. As seen in the boxplot there is an outlier on the right side. It might therefore be a good option to scale the target variable by for example diving it by its standard deviation.

```{r, echo = FALSE, out.width = '40%', out.height = '40%'}
boxplot(dataset1$asst.prof.salary, horizontal = TRUE)
```

#### University
The variable **University** has categorical unique values that contain characters with the universities name.

#### CIC.institutions
The variable **CIC.institutions** has categorical values that are encoded as 0s and 1s. 

```{r, echo = FALSE, warning= FALSE, message= FALSE, out.width = '40%', out.height = '40%'}
ggplot(data = dcast(as.data.table(dataset1$CIC.institutions), formula = V1 ~ .), aes(x = V1, y = .)) + geom_bar(stat = "identity")
```

#### average.salary
The variable **average.salary** is numeric. It's values range from 45.75 to 75.54 with a mean of 58.20 and a median of 56.99. The data does not contain outliers or is skewed it should therefore not be needed to apply preprocessing. (This is of course depening on the used method)

```{r, echo = FALSE, out.width = '40%', out.height = '40%'}
boxplot(dataset1$average.salary, horizontal = TRUE)
```

#### full.prof.salary
The variable **full.prof.salary** is numeric. It's values range from 55.90 to 96.50 with a mean of 73.91 and a median of 72.00. The data does not contain outliers or is skewed it should therefore not be needed to apply preprocessing. (This is of course depening on the used method)

```{r, echo = FALSE, out.width = '40%', out.height = '40%'}
boxplot(dataset1$full.prof.salary, horizontal = TRUE)
```

#### assoc.prof.salary
The variable **assoc.prof.salary** is numeric. It's values range from 41.80 to 70.00 with a mean of 51.43 and a median of 50.65. As seen in the boxplot there is an outlier on the right side. It might therefore be a good option to scale the target variable by for example diving it by its standard deviation.

```{r, echo = FALSE, out.width = '40%', out.height = '40%'}
boxplot(dataset1$assoc.prof.salary, horizontal = TRUE)
```

## Dataset 2